### 2023-04-05 reachable-resilience.tex
up

\begin{theorem}
{\sc state-resilience} is decidable for ideal effective WSTS with downward compatibility,
$\Safe = \downarrow \Safe$ and $\Bad = \uparrow \Bad$.
\end{theorem}

@@

\begin{proposition}
{\sc $k$-state-resilience} and {\sc bounded-state-resilience} are decidable for ideal effective WSTS with strong downward compatibility,
$\Safe = \downarrow \Safe$ and $\Bad = \uparrow \Bad$.
\end{proposition}

@@

\begin{center}
\begin{tabular}{ | l | c | c | c | c |}
\hline  Hypothesis & $\emptyset $ & downward compatible & strongly downward compatible  \\ \hline
   SRP & Undecidable (Thm~\ref{srp down up})  & Decidable   & Decidable \\ \hline
   BSRP & ??  &  ??  & Decidable \\ \hline
      kSRP & ??  & ?? & Decidable  \\ \hline
 \end{tabular}
\end{center}

>>>>

\begin{theorem}\label{downward srp}
{\sc state-resilience} is decidable for ideal effective WSTS with downward compatibility,
$\Safe = \downarrow \Safe$ and $\Bad = \uparrow \Bad$.
\end{theorem}

@@

\begin{proposition}\label{downward brp}
{\sc $k$-state-resilience} and {\sc bounded-state-resilience} are decidable for ideal effective WSTS with strong downward compatibility,
$\Safe = \downarrow \Safe$ and $\Bad = \uparrow \Bad$.
\end{proposition}

@@

\begin{center}
\begin{tabular}{ | l | c | c | c | c |}
\hline  Hypothesis & $\emptyset $ & downward compatible & strongly downward compatible  \\ \hline
   SRP & Undecidable (Thm~\ref{srp down up})  & Decidable (Thm~\ref{downward srp})  & Decidable (Thm~\ref{downward srp}) \\ \hline
   BSRP & ??  &  ??  & Decidable (Prop~\ref{downward brp}) \\ \hline
      kSRP & ??  & ?? & Decidable (Prop~\ref{downward brp}) \\ \hline
 \end{tabular}
\end{center}
